---
title: "KevinFijiAgreementOnNegationAnnotation.Rmd"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Inter-annotator agreement between Kevin and Fiji on CRAFT
## and MIMIC2MD negation annotation


```{r cars}
craft.kevin.data <- read.table("/Users/kev/Dropbox/Negation/Code/CRAFT.type.token.with.prefix.KEVIN.txt", header=F, sep="\t")
craft.fiji.data <- read.table("/Users/kev/Dropbox/Negation/Code/CRAFT.type.token.with.prefix.FIJI.csv", header=F, sep=",")
mimic.kevin.data <- read.table("/Users/kev/Dropbox/Negation/Code/MIMIC2MD.type.token.with.prefix.KEVIN.xls", header=F, sep="\t")
mimic.fiji.data <- read.table("/Users/kev/Dropbox/Negation/Code/MIMIC2MD.type.token.with.prefix.FIJI.annotated.csv", header=F, sep=",")
```
Let's define a function to calculate agreement.  To test it, I calculated my agreement with myself and got 1.0, then my agreement on the two different corpora and got a surprisingly high 0.06!
```{r }
agreement <- function(df.one, df.two) {
  # quick validation
  # this doesn't quit when it should--TODO how do I do this in R??
  if (nrow(df.one) != nrow(df.two)) { quit }
  
  agreements <- 0
  disagreements <- 0
  #judgements <- 0 # calculating agreement only when one or the other 
                  # labelled it
  for (i in 1:nrow(df.one)) {
    if (df.one[i,4] == "x" & df.two[i,4] == "x") {
      agreements <- agreements + 1
    } else if ((df.one[i,4] == "x" & df.two[i,4] != "x") | (df.one[i,4] != "x" & df.two[i,4] == "x")) {
      disagreements <- disagreements + 1
    }
  }
  return (agreements / (agreements + disagreements))
}
```

Let's define another function to calculate agreement, this one considering the ones that neither of us annotated as negative.  To test it, I calculated my agreement with myself and got 1.0.
```{r }
agreement.including.all <- function(df.one, df.two) {
  # quick validation
  # this doesn't quit when it should--TODO how do I do this in R??
  if (nrow(df.one) != nrow(df.two)) { quit }
  
  agreements <- 0
  disagreements <- 0
  #judgements <- 0 # calculating agreement only when one or the other 
                  # labelled it
  for (i in 1:nrow(df.one)) {
    if (df.one[i,4] == df.two[i,4]) {
      agreements <- agreements + 1
    } else {
      disagreements <- disagreements + 1
    }
  }
  return (agreements / (agreements + disagreements))
}
```

## Now let's try to calculate agreement!

```{r}
agreement.craft <- agreement(mimic.kevin.data, mimic.fiji.data)
print("CRAFT IAA (only including ones marked by someone):")
agreement.craft

agreement.mimic <- agreement(craft.kevin.data, craft.fiji.data)
print("MIMIC IAA (as above):")
agreement.mimic

agreement.craft <- agreement.including.all(mimic.kevin.data, mimic.fiji.data)
print("CRAFT IAA (including all):")
agreement.craft

agreement.mimic <- agreement.including.all(craft.kevin.data, craft.fiji.data)
print("MIMIC IAA (as above):")
agreement.mimic

all.kevin.data <- rbind(craft.kevin.data, mimic.kevin.data)
all.fiji.data <- rbind(craft.fiji.data, mimic.fiji.data)
agreement.all <- agreement.including.all(all.kevin.data, all.fiji.data)
print("Overall agreement, including all:")
agreement.all
```

